\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-14 manuscript.Rmd
Added ffiliations

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1"
    corresponding : no   
    address       : "Monash University, Malaysia"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization

  - name          : "Rafael Robert Lazar"
    affiliation   : "2"
    role:
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization
  - name          : "Manuel Spitschan "
    affiliation   : "3"
    corresponding : yes   
    address       : ""
    email         : ""
    role:         
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia"
  - id            : "2"
    institution   : "University of Basel"

>>>>

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, *"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Formal Analysis
      - Visualization
      - Writing – original draft

  - name          : "Rafael Robert Lazar"
    affiliation   : "2, 3, *"
    role:
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "4"
    email         : "j.v.duijnhoven1@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "5"
    email         : "l.j.m.schlangen@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Shamsul Haque"
    affiliation   : "1"
    email         : "shamsul@monash.edu"
    role:         
      - Conceptualization
      - Supervision
      - Writing – review & editing

  - name          : "Vineetha Kalavally"
    affiliation   : "6"
    email         : "vineetha@monash.edu"
    role:         
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "7, 8"
    email         : "celine.vetter@colorado.edu"
    role:         
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "9"
    email         : "gena.glickman@usuhs.edu"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "10"
    email         : "k.c.h.j.smolders@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 2, 3"
    email         : "manuel.spitschan@psy.ox.ac.uk"
    role:         
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
  - id            : "7"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "8"
    institution   : "Ximes GmbH, Frankfurt, Germany"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
  - id            : "11"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
  - id            : "*"
    institution   : "Joint first author"
